### 2012-05-12 docs/matching_algo/matching_algo.tex
writing more on matching

@@

@@

\subsection{Postconditions}
These are true for the match state that results from each successful branch:
\begin{itemize}
\item $U_c = U_w = U_n = P = \varnothing$ (we cleaned up after ourselves)
\item $P$ is exactly the set of vertices in $\dom(m)$ that are adjacent to a vertex not in $\dom(m)$ ($P$ contains exactly the partially-matched vertices)
\item $\dom(m)$ is the union of the initial states of $U_c$, $U_w$, $U_n$ and $\dom(m)$ (we have matched everything we were asked to, and not lost anything in the process)
\item $m$ induces a graph monomorphism from the full subgraph of $L$ described by $\dom(m)$ to the full subgraph of $G$ described by $\codom(m)$ ($m$ is actually a partial matching from $L$ to $G$)
\end{itemize}

\section{Outer Loop: Pattern Expansion}

>>>>

Note that circles are given as the name of smallest wire-vertex in the circle, w.r.t. the name ordering.

@@

The concrete matching routine is given a function ``doomed'', which returns true if a match of a concrete node-vertex is impossible. For !-box matching this returns true if the (concrete) neighbourhood of $v$ contains fewer in-edges (resp. out-edges) than that of $m(v)$ and there are no !-boxes connected to $v$ by an in-edge (resp. out-edge). It also takes a match state, subject to the following preconditions:

@@

\subsection{Postconditions}
These are true for the match state that results from each successful branch:
\begin{itemize}
  \item $U_c = U_w = U_n = P_s = \varnothing$ (every vertex marked for matching was handled)
  \item $m$ is a partial matching from $L$ to $G$ that satisfies local iso condition for concrete vertices not in $P$,
  \item $P$ is exactly the set of vertices in $\dom(m)$ that are adjacent to a vertex not in $\dom(m)$ ($P$ contains exactly the partially-matched vertices)
  \item $\dom(m)$ is the union of the initial states of $U_c$, $U_w$, $U_n$ and $\dom(m)$ (we have matched everything we were asked to, and not lost anything in the process)
\end{itemize}

\section{Testing Wrapper: Concrete Matching Only}

For testing purposes, it is straight-forward to wrap the above procedure to just do concrete matching.

\begin{center}
  \includegraphics[height=12cm]{concrete_wrapper.pdf}
\end{center}

\section{Full Wrapper: Lazy !-Box Expansion}

Since we are only matching !-graphs on to concrete graphs, it suffices to restrict !-box operations to only two: KILL and EXPAND (COPY, then DROP the new box).
